---
title: "Primary and Secondary Analysis"
author: |
    |
date: '`r format(Sys.Date(), "%B %d, %Y")`'
geometry: margin=0.5in
classoption: landscape
output: 
  pdf_document:
    number_sections: TRUE
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(width = 120)
```



```{r, echo = FALSE, warning=FALSE, message = FALSE}
library(dplyr)
library(readxl)
library(lubridate)

source("paths.R")
source("estimator.R")
```



```{r, echo = FALSE, warning=FALSE, message = FALSE}
load(file.path(path_staged_data, "dat_analysis.RData"))

# This step might appear unnecessary, but is needed since
# dat_analysis is both a tibble and a data frame
# but code in estimator.R does not work with tibbles
# The call to as.data.frame() has the effect of making
# dat_analysis of class data frame but not of class tibble
dat_analysis <- as.data.frame(dat_analysis)
```

```{r, echo = FALSE, warning=FALSE, message = FALSE}
table01 <- dat_analysis %>%
    filter(exclude_from_all==0) %>%
    filter(coinflip==1) %>%
    group_by(decision_point) %>%
    summarise(count_randomized = n(),
              proportion_responded_within47hours = mean(Y_delta47),
              proportion_randomized_to_product = mean(1*(randassign_invite=="Product")))
```


Among the 591 participants who were randomized to the experimental condition, exclude participants who

* did not specify either their preferred product or charity at baseline 


```{r, echo = FALSE, warning=FALSE, message = FALSE}
print(table01)
```

\newpage

# Participants and decision points used to estimate causal effect

```{r, echo = FALSE, warning=FALSE, message = FALSE}
table02 <- dat_analysis %>%
    filter(exclude_from_all==0) %>%
    filter(coinflip==1) %>%
    filter(did_not_report_primary_analysis_vars==0) %>%
    group_by(decision_point) %>%
    summarise(count_randomized = n(),
              proportion_responded_within47hours = mean(Y_delta47),
              proportion_randomized_to_product = mean(1*(randassign_invite=="Product")))

table03 <- dat_analysis %>%
    filter(exclude_from_all==0) %>%
    filter(coinflip==1) %>%
    filter(did_not_report_secondary_analysis_vars==0) %>%
    group_by(decision_point) %>%
    summarise(count_randomized = n(),
              proportion_responded_within47hours = mean(Y_delta47),
              proportion_randomized_to_product = mean(1*(randassign_invite=="Product")))
```


Among the 591 participants who were randomized to the experimental condition, exclude participants who

* did not specify either their preferred product or charity at baseline 
* had a missing value in any of the variables utilized in the noise reduction model; that is, the variables:
  - tot_days_with_any_drinks
  - typical_num_drinks_per_day
  - is_female
  - is_white_only

```{r, echo = FALSE, warning=FALSE, message = FALSE}
print(table02)
```


Among the 591 participants who were randomized to the experimental condition, exclude participants who

* did not specify either their preferred product or charity at baseline 
* had a missing value in any of the variables utilized in the noise reduction model; that is, the variables:
  - tot_days_with_any_drinks
  - typical_num_drinks_per_day
  - is_female
  - is_white_only
* had a missing value in any of the variables utilized in the model for the causal effect; that is, the variables:
  - baseline_anxiety
  - baseline_depression
  - baseline_stress


```{r, echo = FALSE, warning=FALSE, message = FALSE}
print(table03)
```



```{r, echo = FALSE, warning=FALSE, message = FALSE}
# The software expects that intervention assignment is coded as numeric, 
# and not character type
dat_analysis <- dat_analysis %>% 
  filter(exclude_from_all == 0) %>% 
  mutate(randassign_invite = case_when(
    randassign_invite == "Product" ~ 1,
    randassign_invite == "Charity" ~ 0,
    TRUE ~ NA_real_))
```


\newpage

# Estimate of causal effect for Hypothesis 1



```{r, echo=FALSE, warning=FALSE, message=FALSE}
# Data preparation steps for primary analysis
these_vars <- c("tot_days_with_any_drinks", 
                "typical_num_drinks_per_day",
                "is_female", 
                "is_male", 
                "is_white_only",
                "days_elapsed_since_entering")

dat_primary_analysis <- dat_analysis %>%
  # Drop participants who had any missing data in these_vars
  filter(did_not_report_primary_analysis_vars == 0) %>%
  select(participant_id, 
         decision_point, 
         randassign_invite, 
         coinflip, 
         Y_delta47,
         all_of(these_vars))
```



```{r, echo=FALSE, warning=FALSE, message=FALSE}
# Data preparation steps for secondary analysis
these_vars <- c("tot_days_with_any_drinks", 
                "typical_num_drinks_per_day",
                "is_female", 
                "is_male", 
                "is_white_only",
                "days_elapsed_since_entering",
                "baseline_anxiety", 
                "baseline_depression", 
                "baseline_stress")

dat_secondary_analysis <- dat_analysis %>%
  # Drop participants who had any missing data in these_vars
  filter(did_not_report_secondary_analysis_vars == 0) %>%
  select(participant_id, 
         decision_point, 
         randassign_invite, 
         coinflip, 
         Y_delta47,
         all_of(these_vars))
```



```{r, echo=FALSE, warning=FALSE, message=FALSE}
list_results_H1 <- binary_outcome_moderated_effect(dta = dat_primary_analysis, 
                                                   control_var = c("tot_days_with_any_drinks", 
                                                                   "typical_num_drinks_per_day", 
                                                                   "is_white_only",
                                                                   "is_female", 
                                                                   "is_male", 
                                                                   "days_elapsed_since_entering"),
                                                   moderator = NULL,
                                                   id_var = "participant_id",
                                                   day_var = "decision_point",
                                                   trt_var = "randassign_invite",
                                                   outcome_var = "Y_delta47",
                                                   avail_var = "coinflip",
                                                   prob_treatment = 1/2,
                                                   significance_level = 0.05)


significance_level <- 0.05
p <- list_results_H1[["dims"]]$p
q <- list_results_H1[["dims"]]$q
n <- list_results_H1[["sample_size"]]
all_estimates <- c(list_results_H1[["alpha_hat"]], list_results_H1[["beta_hat"]])
all_std_err <- c(list_results_H1[["alpha_se_ssa"]], list_results_H1[["beta_se_ssa"]])
test_stat <- all_estimates / all_std_err
critical_value <- qt(1 - significance_level/2, df = n - p - q) # two-sided
p_val <- lapply(test_stat, function(x){
  out <- 2 * pt(abs(x), df = n - p - q, lower.tail = FALSE) # two-sided
  return(out)
})
p_val <- do.call(rbind, p_val)

dat_results_H1 <- data.frame(exp_estimate = exp(all_estimates),
                             estimate = all_estimates,
                             std_err = all_std_err,
                             p = p_val,
                             LB95 = all_estimates - critical_value*all_std_err,
                             UB95 = all_estimates + critical_value*all_std_err)

dat_results_H1 <- round(dat_results_H1, digits = 3)
row.names(dat_results_H1) <- c("Intercept", 
                               "No. of Days with any drinks", 
                               "No. of Drinks per day", 
                               "White (1=Yes, 0=otherwise)", 
                               "Female (1=Yes, 0=otherwise)",
                               "Male (1=Yes, 0=otherwise)",
                               "No. of Days elapsed since entering",
                               "beta0")
```



```{r, echo=FALSE, warning=FALSE, message=FALSE}
print(dat_results_H1)
```



# Estimate of causal effect for Hypothesis 2



```{r, echo=FALSE, warning=FALSE, message=FALSE}
list_results_H2 <- binary_outcome_moderated_effect(dta = dat_secondary_analysis, 
                                                   control_var = c("tot_days_with_any_drinks", 
                                                                   "typical_num_drinks_per_day", 
                                                                   "is_white_only",
                                                                   "is_female", 
                                                                   "is_male", 
                                                                   "days_elapsed_since_entering"),
                                                   moderator = c("baseline_anxiety", 
                                                                 "baseline_depression", 
                                                                 "baseline_stress"),
                                                   id_var = "participant_id",
                                                   day_var = "decision_point",
                                                   trt_var = "randassign_invite",
                                                   outcome_var = "Y_delta47",
                                                   avail_var = "coinflip",
                                                   prob_treatment = 1/2,
                                                   significance_level = 0.05)


significance_level <- 0.05
p <- list_results_H2[["dims"]]$p
q <- list_results_H2[["dims"]]$q
n <- list_results_H2[["sample_size"]]
all_estimates <- c(list_results_H2[["alpha_hat"]], list_results_H2[["beta_hat"]])
all_std_err <- c(list_results_H2[["alpha_se_ssa"]], list_results_H2[["beta_se_ssa"]])
test_stat <- all_estimates / all_std_err
critical_value <- qt(1 - significance_level/2, df = n - p - q) # two-sided
p_val <- lapply(test_stat, function(x){
  out <- 2 * pt(abs(x), df = n - p - q, lower.tail = FALSE) # two-sided
  return(out)
})
p_val <- do.call(rbind, p_val)

dat_results_H2 <- data.frame(exp_estimate = exp(all_estimates),
                             estimate = all_estimates,
                             std_err = all_std_err,
                             p = p_val,
                             LB95 = all_estimates - critical_value*all_std_err,
                             UB95 = all_estimates + critical_value*all_std_err)

dat_results_H2 <- round(dat_results_H2, digits = 3)
row.names(dat_results_H2) <- c("Intercept", 
                               "No. of Days with any drinks", 
                               "No. of Drinks per day", 
                               "White (1=Yes, 0=otherwise)", 
                               "Female (1=Yes, 0=otherwise)",
                               "Male (1=Yes, 0=otherwise)",
                               "No. of Days elapsed since entering",
                               "beta0",
                               "beta1 (Coefficient for treatment x baseline anxiety)",
                               "beta2 (Coefficient for treatment x baseline depression)",
                               "beta3 (Coefficient for treatment x baseline stress)")

```



```{r, echo=FALSE, warning=FALSE, message=FALSE}
print(dat_results_H2)
```



