---
title: "Results"
author: |
    |
date: '`r format(Sys.Date(), "%B %d, %Y")`'
geometry: margin=1in
output: 
  pdf_document:
    number_sections: TRUE
---

```{r, echo = FALSE, message = FALSE}
library(dplyr)
library(readxl)

path_input_data <- Sys.getenv("path_input_data")
path_staged_data <- Sys.getenv("path_staged_data")

source(file.path("run-analysis-exploratory.R"))
```

```{r}
print(dat_summary)
```

# Outcome: Y=1 if classified as non-responder by 1st decision point; Y=0 otherwise

```{r}
summary(mod_flagged_by_01a)
```

```{r}
summary(mod_flagged_by_01b)
```

# Outcome: Y=1 if classified as non-responder by 2nd decision point (i.e., classified as non-responder at either 1st or 2nd decision point); Y=0 otherwise

```{r}
summary(mod_flagged_by_02a)
```

```{r}
summary(mod_flagged_by_02b)
```


# Outcome: Y=1 if classified as non-responder by 3rd decision point (i.e., classified as non-responder at either 1st, 2nd, or 3rd decision point); Y=0 otherwise

```{r}
summary(mod_flagged_by_03a)
```

```{r}
summary(mod_flagged_by_03b)
```


# Outcome: Y=1 if classified as non-responder by 4th decision point (i.e., classified as non-responder at either 1st, 2nd, 3rd, or 4th decision point); Y=0 otherwise (i.e., never classified as non-responder throughout the study)

```{r}
summary(mod_flagged_by_04a)
```

```{r}
summary(mod_flagged_by_04b)
```




